Bayesian Nonparametric Neural Image Segmentation

### 2013-02-06 latex/submission.tex
fixed refs

Feature engineering significantly shapes the state of the art. Venkataraju et al. \cite{Venkataraju2009} generated 100 Hessian neighborhood features at each pixel and classified Jurrus's dataset with AdaBoost. Lucchi et al. \cite{Lucchi2010} develop ray descriptors, which capture shape features without a predefined shape model. These features are rotation, scale, and translation invariant, but strongly discriminate the types of objects observed in EM images. There features were used in SVMs to classify interior and boundary points of mitochondria, considerably harder to classify than other cellular structures \cite{Kaynig2010b}, and a graph cut found the final 2D segmentation with 98\% accuracy.

>>>>

Feature engineering significantly shapes the state of the art. Venkataraju et al. \cite{Venkataraju2009} generated 100 Hessian neighborhood features at each pixel and classified Jurrus's dataset with AdaBoost. Lucchi et al. \cite{Lucchi2010} develop ray descriptors, which capture shape features without a predefined shape model. These features are rotation, scale, and translation invariant, but strongly discriminate the types of objects observed in EM images. Their features were used in SVMs to classify interior and boundary points of mitochondria, considerably harder to classify than other cellular structures, and a graph cut found the final 2D segmentation with 98\% accuracy.
